Model details

### 2023-03-08 analysis/model-details.qmd
Include code for fun

```{r calculate-model-times, include=FALSE}
model_times <- bind_rows(list("**Preliminary models: Derogations and emergency policies**" = m_prelim_derog, 
                              "**H<sub>1</sub>: Derogations and human rights**" = m_h1, 
                              "**H<sub>2</sub>: Derogations, civil society, and human rights**" = m_h2), 
                         .id = "hypothesis") %>%  
  mutate(family = case_when(
    family == "cumulative" ~ "Ordered logistic",
    family == "bernoulli" | is.na(family) ~ "Logistic"
  )) %>% 
  mutate(duration = map(model, ~{
    .$fit %>% 
      rstan::get_elapsed_time() %>% 
      as_tibble() %>% 
      summarize(total = as.duration(max(warmup + sample)))
  })) %>% 
  select(-prior, -y, -never, -data, -model) %>% 
  unnest(duration)

>>>>

```{r calculate-model-times}
model_times <- bind_rows(list("**Preliminary models: Derogations and emergency policies**" = m_prelim_derog, 
                              "**H<sub>1</sub>: Derogations and human rights**" = m_h1, 
                              "**H<sub>2</sub>: Derogations, civil society, and human rights**" = m_h2), 
                         .id = "hypothesis") %>%  
  mutate(family = case_when(
    family == "cumulative" ~ "Ordered logistic",
    family == "bernoulli" | is.na(family) ~ "Logistic"
  )) %>% 
  mutate(duration = map(model, ~{
    .$fit %>% 
      rstan::get_elapsed_time() %>% 
      as_tibble() %>% 
      summarize(total = as.duration(max(warmup + sample)))
  })) %>% 
  select(-prior, -y, -never, -data, -model) %>% 
  unnest(duration)
